---
title: 'Proof CJ: Judgement data'
author: "George Kinnear"
date: "22/03/2021"
always_allow_html: true
output:
  github_document:
    html_preview: false
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path='figs-web/01-judgements/')

library(tidyverse)

# Tables
library(knitr)
library(kableExtra)
basic_kable = function(df) {
  df %>% 
    kable() %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}
rmarkdown::html_document(df_print = knitr::kable)

# Set preferred styling
theme_set(theme_minimal())
```


```{r read-data, echo=FALSE, message = FALSE}
if(file.exists("data-out/judgement_data_all.csv") && file.exists("data-out/script_info.csv")) {
  # Read the cached data
  judgement_data_all <- read_csv("data-out/judgement_data_all.csv")
  script_info <- read_csv("data-out/script_info.csv")
  print("Data loaded from data-out folder")
} else {
  
  # Gather, anonymise, and cache the data
  
  # Find all the CSV files for this study
  study_files <- fs::dir_ls(path = "data-study-1", regexp = ".*.csv")
  study_files <- c(study_files, fs::dir_ls(path = "data-study-2", regexp = ".*.csv"))
  
  # Assemble the csv data into a large nested table
  # - this assumes filenames provide logical info in the form dimension_info.csv, where:
  #   * dimension - is the concept they were working with - one of the following:
  dimensions_sorted <- c("rigour", "insight", "simple", "understanding", "marks")
  #   * info - is the type of data in the csv, either judgements, definitions or judges details
  study_dfs <- tibble(path = study_files) %>%
    separate(
      path,
      into = c("study", "filename"),
      sep = "/",
      remove = FALSE
    ) %>%
    mutate(
      filename = str_replace(filename, ".csv", ""),
      study = paste0("study", str_sub(study,-1))
    ) %>% 
    separate(filename, into = c("dimension", "info"), sep = "_") %>% 
    mutate(
      csv_content = purrr::map(path, read_csv)
    ) %>% 
    mutate(dimension = fct_relevel(dimension, dimensions_sorted)) %>% 
    arrange(study, dimension)
  
  judgement_data_all <- study_dfs %>% 
    filter(info == "judgements") %>% 
    select(study, dimension, csv_content) %>% 
    unnest(cols = c(csv_content))
  
  script_info <- study_dfs %>% 
    filter(info == "scripts") %>% 
    select(study, dimension, csv_content) %>% 
    unnest(cols = c(csv_content))
  
  judgement_data_all %>% write_csv("data-out/judgement_data_all.csv")
  script_info %>% write_csv("data-out/script_info.csv")
}
proof_names <- script_info %>% 
  select(id = `Submission id`, proof = `Full name`)

proof_names %>% write_csv("data-out/proof_names.csv")

proof_details <- read_csv("proof-details.csv")
```


# Summary of the decision data

## Judges summary


```{r}
judge_summary <- judgement_data_all %>% 
  select(study, dimension, JudgeID) %>% 
  group_by(study, dimension, JudgeID) %>% 
  tally(name = "judgements_made") %>% 
  group_by(study, dimension, judgements_made) %>% 
  summarise(
    num_judges = n(),
    judges = paste0(JudgeID, collapse = ", "),
    .groups = "drop"
  )

judge_summary %>% 
  group_by(study, dimension) %>% 
  tally(num_judges, name = "num_judges") %>% 
  kable(booktabs = T) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>% 
  collapse_rows(columns = 1, valign = "top")

```

## Judgements per judge

```{r echo=FALSE, fig.height=5, fig.width=10}
judgement_data_all %>%
  select(study, dimension, JudgeID) %>%
  group_by(study, dimension, JudgeID) %>%
  tally(name = "judgements_made") %>%
  group_by(study, dimension) %>%
  arrange(-judgements_made) %>%
  mutate(row_num = row_number()) %>%
  ungroup() %>%
  full_join(
    judgement_data_all %>% select(study, dimension) %>% distinct() %>% crossing(tibble(row_num = c(1:50))),
    by = c("study", "dimension", "row_num")
  ) %>% 
  mutate(judgements_made = replace_na(judgements_made, 0), JudgeID = replace_na(JudgeID, "")) %>% 
  mutate(JudgeID = fct_reorder(as.factor(JudgeID), judgements_made)) %>% 
  ggplot(aes(x = row_num, y = judgements_made)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  facet_wrap(facets = vars(study, dimension), scales = "free", nrow = 1)
```

```{r echo=FALSE, fig.height=5, fig.width=10}
judgement_data_all %>%
  select(study, dimension, JudgeID) %>%
  group_by(study, dimension, JudgeID) %>%
  tally(name = "judgements_made") %>%
  ungroup() %>%
  mutate(JudgeID = fct_reorder(as.factor(JudgeID), judgements_made)) %>% 
  ggplot(aes(x = JudgeID, y = judgements_made)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  facet_wrap(facets = vars(study, dimension), scales = "free", nrow = 1)
```


## Time taken

```{r echo=FALSE, warning=FALSE}
judgement_data_all %>% 
  ggplot(aes(x = TimeTaken)) +
  geom_histogram(binwidth = 1) +
  xlim(0,60) +
  labs(title = "Histogram of times for each judgement", subtitle = "Trimmed at 60s")

judgement_data_all %>% 
  group_by(JudgeID) %>% 
  summarise(median_TimeTaken = median(TimeTaken)) %>% 
  ggplot(aes(x = median_TimeTaken)) +
  geom_histogram(binwidth = 1) +
  xlim(0,60) +
  labs(title = "Histogram of median judgement time for each judge")
```

Judges became progressively quicker at making decisions as judging went on:

```{r}
judgement_data_all %>% 
  group_by(JudgeID) %>% 
  mutate(judgement_num = row_number()) %>% 
  group_by(judgement_num) %>% 
  summarise(
    mean = mean(TimeTaken),
    median = median(TimeTaken)
  )

judgement_data_all %>% 
  group_by(JudgeID) %>% 
  mutate(judgement_num = row_number()) %>% 
  mutate(judgement_num = as.factor(judgement_num)) %>% 
  ggplot(aes(x = judgement_num, y = TimeTaken)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 120))
```

By study:

```{r}
judgement_data_all %>% 
  group_by(JudgeID) %>% 
  mutate(judgement_num = row_number()) %>% 
  group_by(study, judgement_num) %>% 
  summarise(
    mean = mean(TimeTaken),
    median = median(TimeTaken)
  )

judgement_data_all %>% 
  group_by(JudgeID) %>% 
  mutate(judgement_num = row_number()) %>% 
  mutate(judgement_num = as.factor(judgement_num)) %>% 
  ggplot(aes(x = judgement_num, y = TimeTaken, fill = study)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 120))
```

Median judgement times per study:

```{r}
judgement_data_all %>%
  group_by(study) %>% 
  summarise(median_TimeTaken = median(TimeTaken)) %>% 
  basic_kable()
```

Filtering out nonserious judges, whose median judgement time is under 5 seconds.

```{r warning=FALSE}
judge_times <- judgement_data_all %>% 
  group_by(JudgeID) %>% 
  summarise(median_TimeTaken = median(TimeTaken)) %>% 
  mutate(nonserious_judge = median_TimeTaken < 5)

judge_times %>% 
  janitor::tabyl(nonserious_judge) %>% 
  basic_kable()

judgement_data_all %>% 
  left_join(judge_times, by = "JudgeID") %>% 
  mutate(study_dim = paste(study, dimension)) %>% 
  janitor::tabyl(study_dim, nonserious_judge) %>%
  janitor::adorn_percentages("row") %>%
  janitor::adorn_pct_formatting(digits = 2) %>%
  janitor::adorn_ns() %>%
  janitor::adorn_title(placement = "top", col_name = "Judgements to be discarded") %>% 
  basic_kable()

judgement_data <- judgement_data_all %>% 
  left_join(judge_times, by = "JudgeID") %>% 
  filter(nonserious_judge == FALSE) %>% 
  select(-nonserious_judge, -median_TimeTaken)
  
judgement_data %>% 
  left_join(judge_times, by = "JudgeID") %>% 
  group_by(study, dimension, JudgeID, median_TimeTaken) %>% 
  summarise(num_judgements = n(), .groups = "drop") %>% 
  ggplot(aes(x=num_judgements, y = median_TimeTaken)) +
  geom_point(position = "jitter", alpha = 0.5) +
  facet_wrap(vars(study, dimension)) +
  ylim(0,200)
```



## Summary of the filtered judgements

```{r echo=FALSE}
long_decisions <- judgement_data %>% 
  pivot_longer(cols = c(Won, Lost), names_to = "side", values_to = "script")
```

```{r echo=FALSE}
long_decisions %>% 
  group_by(study, dimension, script) %>% 
  summarise(
    judgements = n(),
    wins = sum(side=="Won"),
    losses = sum(side=="Lost"),
    .groups = "drop"
  ) %>% 
  left_join(proof_names, by = c("script" = "id")) %>% 
  relocate(proof, .after = "script") %>% 
  arrange(study, dimension, proof) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
  collapse_rows(columns = 1:2, valign = "top")
```

# Save data

Filtered judgement data written to `data-out/judgement_data.csv`.

```{r}
judgement_data %>% 
  write_csv("data-out/judgement_data.csv")
```