---
title: "Proof CJ: Study 2 analysis"
author: "George Kinnear"
date: "22/03/2021"
always_allow_html: true
output:
  github_document:
    html_preview: false
  html_document:
    toc: false
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path='figs-web/05-study2-analysis/')

# for plotting
library(ggrepel)
source("functions_for_plotting.R")
theme_set(theme_minimal())
library(patchwork)

library(knitr)
library(kableExtra)
basic_kable = function(df) {
  df %>% 
    kable() %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}

dimensions_sorted <- c("rigour", "insight", "simple", "understanding", "marks")

# For the Bayesian stuff
library(bayestestR)
library(insight)
library(BayesFactor)
ci_width <- 0.95
set.seed(22032021)
```


```{r echo=FALSE, fig.height=1, fig.width=8, message=FALSE}
btm_estimates <- read_csv("data-out/btm_estimates.csv") %>% 
  mutate(dimension = fct_relevel(dimension, dimensions_sorted)) %>% 
  filter(study == "study2") %>% 
  select(-study)

proof_details <- read_csv("proof-details.csv")

proofs_legend_content <- proof_details %>% 
  mutate(proof_name = str_glue("{proof}. {proof_name}")) %>% 
  mutate(proof_name = fct_reorder(proof_name, proof))

# Legend showing the names of the proofs
proofs_legend_plot <- proofs_legend_content  %>% 
  ggplot(aes(x = proof, y = proof)) +
  geom_text(aes(colour = proof_name, label = proof_name),
            show.legend = TRUE,
            key_glyph = draw_key_blank) +
  guides(colour = guide_legend(
    title = "",
    ncol = 5,
    byrow = FALSE,
    override.aes = aes(label = "")
  )) +
  theme(legend.key.width = unit(0, "cm"), legend.box.margin = margin(6, 6, 6, 6))

proofs_legend <- proofs_legend_plot %>% ggpubr::get_legend() %>% ggpubr::as_ggplot()
proofs_legend
ggsave("figs/FIG_study2-proofs-legend.pdf", width = 22, height = 3, units = "cm")
```

# Basic plots of the scales

The scale values with standard errors:

```{r}
btm_estimates %>% 
  filter(!dimension %in% c("words", "string_length")) %>%
  group_by(dimension) %>% 
  arrange(theta) %>% 
  mutate(order = row_number()) %>% 
  ggplot(aes(x = order, y = theta, ymin = theta - se, ymax = theta + se)) +
  geom_hline(yintercept = 0, colour = "grey") +
  geom_pointrange(size = 0.25) +
  geom_text_repel(aes(label = proof), box.padding = 0.3, min.segment.length = 0.5, colour = "#777777") +
  facet_grid(cols = vars(dimension), scales = "free") +
  theme(
    axis.text.x = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold"),
  ) +
  labs(x = "")
ggsave("figs/FIG_study2-thetas-samescale.pdf", width = 25, height = 10, units = "cm")

plot_thetas <- btm_estimates %>% 
  filter(!dimension %in% c("words", "string_length")) %>%
  group_by(dimension) %>% 
  arrange(theta) %>% 
  mutate(order = row_number()) %>% 
  ggplot(aes(x = order, y = theta, ymin = theta - se, ymax = theta + se)) +
  geom_hline(yintercept = 0, colour = "grey") +
  geom_pointrange(size = 0.25) +
  geom_text_repel(aes(label = proof), box.padding = 0.3, min.segment.length = 0.5, colour = "#777777", size = 3) +
  facet_wrap(facets = vars(dimension), scales = "free", ncol = 5) +
  theme(
    axis.text.x = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold"),
  ) +
  labs(x = "")
(plot_thetas) / proofs_legend + 
  plot_layout(widths = c(1, 1), heights = unit(c(7, 2), c('cm', 'cm')))
ggsave("figs/FIG_study2-thetas.pdf", width = 22, height = 11, units = "cm")
```


```{r}
# Assemble data
alldims_theta_se <- btm_estimates %>% 
  rbind(
    proof_details %>% 
      select(proof, words, string_length) %>% 
      pivot_longer(
        cols = c("words", "string_length"),
        names_to = "dimension",
        values_to = "theta"
      ) %>% 
      mutate(se = 0)
  )

crossdims <- alldims_theta_se %>% 
  left_join(alldims_theta_se, by = "proof", suffix = c("_x", "_y")) %>% 
  filter(dimension_x != dimension_y)
```


# Bayesian stats

```{r}
dimensions_tbl <- tibble(dimension = c(dimensions_sorted, "words", "string_length")) %>% mutate(n = row_number())
upper_triang <- dimensions_tbl %>% 
  rename(dimension_y = dimension, n_y = n) %>% 
  crossing(dimensions_tbl) %>% 
  rename(dimension_x = dimension, n_x = n) %>% 
  filter(n_x > n_y) %>% 
  arrange(n_y, n_x) %>% 
  select(contains("dimension"))

crossdims_upper_triangular <- crossdims %>%
 semi_join(upper_triang, by = c("dimension_x", "dimension_y"))

# Bayes factor interpretations from van Doorn et al. (2020) https://doi.org/10.3758/s13423-020-01798-5
vandoorn2020 <- effectsize::rules(c(3, 30), c("weak", "moderate", "strong"))
# pick colours for these - avoiding the extremes of the scale, which are too dark
bayes_interp_cols = colorspace::diverging_hcl(8, "Green-Brown")[2:7]
names(bayes_interp_cols) = c("strong in favour of",
                             "moderate in favour of",
                             "weak in favour of",
                             "weak against",
                             "moderate against",
                             "strong against")
```

Do a Bayesian correlation test on each combination, and describe the resulting posteriors.

```{r}
bayes_corrs <- crossdims_upper_triangular %>%
  group_by(dimension_x, dimension_y) %>%
  nest() %>%
  # This step does the Bayesian test.
  # rscale = "ultrawide" specifies uniform (i.e. Beta(1,1)) priors
  mutate(
    model = map(
      data,
      ~ BayesFactor::correlationBF(.$theta_x, .$theta_y, rscale = "ultrawide")
    ),
    posterior = map(model, ~ bayestestR::describe_posterior(., ci = ci_width))
  ) %>%
  select(`dimension_x`, `dimension_y`, posterior) %>%
  unnest(cols = c(posterior)) %>%
  arrange(-BF) %>%
  # interpret Bayes factors in line with van Doorn et al. (2020) https://doi.org/10.3758/s13423-020-01798-5
  mutate(interpretation = effectsize::interpret_bf(BF, rules = vandoorn2020)) %>%
  mutate(interpretation = str_replace(interpretation, "evidence ", "")) %>%
  mutate(interpretation = factor(interpretation, levels = names(bayes_interp_cols)))
  
  
coef_table <- bayes_corrs %>% 
  relocate(interpretation, BF) %>% 
  mutate(hdi = paste0("[", round(CI_low, 2), ", ", round(CI_high, 2), "]")) %>%
  #filter(!dimension_x %in% c("string_length", "words"))
  identity()

coef_table %>%
  select(interpretation,
         BF,
         contains("dimension"),
         Median,
         hdi) %>%
  mutate(Visualisation = "") %>%
  kbl(
    booktabs = T,
    digits = 2,
    col.names = c(
      "Interpretation",
      "BF",
      "Dimension 1",
      "Dimension 2",
      "Median",
      paste0(0.95 * 100, "% HDI"),
      "Visualisation"
    )
  ) %>%
  kable_styling(
    bootstrap_options = "striped",
    full_width = F,
    position = "left"
  ) %>%
  column_spec(
    7,
    image = spec_pointrange(
      x = coef_table$Median,
      xmin = coef_table$CI_low,
      xmax = coef_table$CI_high,
      vline = 0,
      cex = 0.5
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

This shows there is no evidence of the string/word length correlating with the scales, and that there is a reasonable correlation between the scales.

Here is the detail on the correlation between judging scales:

```{r}
coef_table %>%
  filter(!dimension_x %in% c("string_length", "words")) %>%
  ungroup() %>%
  select(starts_with("dimension"), Median, hdi, BF, interpretation) %>%
  mutate(
    interpretation = paste(interpretation),
    # hack! to convert it to a string
    interpretation = if_else(
      lag(interpretation, n = 1) == (interpretation),
      "",
      interpretation,
      interpretation
    )
  ) %>%
  kbl(
    booktabs = T,
    digits = 2,
    col.names = c(
      "Dimension 1",
      "Dimension 2",
      "Median",
      paste0(ci_width * 100, "% HDI"),
      "BF",
      "Interpretation"
    )
  ) %>%
  kable_styling(full_width = F,
                position = "left")
```

## Correlation summary plot

```{r}
# This is based on frequentist stats, but we can hack it to use our Bayesian numbers
library(corrplot)

dimensions_corr_order = c("marks", "rigour", "insight", "understanding", "simple")

just_corrs = coef_table %>% 
  filter(!dimension_x %in% c("string_length", "words")) %>%
  ungroup() %>%
  select(starts_with("dimension"), Median)

M = just_corrs %>%
  right_join(
    crossing(dimension_x = dimensions_sorted,
             dimension_y = dimensions_sorted),
    by = c("dimension_x", "dimension_y")
  ) %>%
  # add on the mirror image over the diagonal
  left_join(
    just_corrs %>% rename(tmp = dimension_x, dimension_x = dimension_y) %>% rename(dimension_y = tmp),
    by = c("dimension_x", "dimension_y")
  ) %>%
  # consolidate the Median columns, and fill in the diagonal with 1's
  mutate(Median = coalesce(Median.x, Median.y, 1), .keep = "unused") %>%
  # reshape and put the rows/cols in the right order
  pivot_wider(names_from = dimension_y,
              values_from = Median) %>%
  arrange(factor(dimension_x, levels = dimensions_sorted)) %>%
  relocate(all_of(dimensions_sorted)) %>%
  column_to_rownames(var = "dimension_x") %>%
  mutate(across(everything(), ~ replace_na(., 0))) %>%
  as.matrix()

pdf(file = "figs/FIG_study2-corrplot.pdf")
corrplot(M,
         type="upper",
         method = "square",
         order = "AOE",
         tl.col="black", tl.srt=0, 
         addCoef.col = "black", # Add coefficient of correlation
         diag = FALSE,
         col = rev(bayes_interp_cols),
         #p.mat = p.mat, sig.level = 0.005, # testing 10 correlations, so use alpha = 0.05 / 10
         #insig = "blank"
         )
dev.off()
corrplot(M,
         type="upper",
         method = "square",
         order = "AOE",
         tl.col="black", tl.srt=0, 
         addCoef.col = "black", # Add coefficient of correlation
         diag = FALSE,
         col = rev(bayes_interp_cols),
         #p.mat = p.mat, sig.level = 0.005, # testing 10 correlations, so use alpha = 0.05 / 10
         #insig = "blank"
         )
```


## Summary plots

```{r fig.height=10, fig.width=10, warning=FALSE}
plot_bayes_corr_grid(crossdims_upper_triangular, bayes_corrs)
ggsave("figs/FIG_study2-correlation-summary-bayes-full.pdf", width = 27, height = 20, units = "cm")
```

```{r, warning=FALSE}
plot_bayes_corr_grid(
  crossdims_upper_triangular %>% filter(!dimension_x %in% c("string_length", "words")),
  bayes_corrs %>% filter(!dimension_x %in% c("string_length", "words"))
)
ggsave("figs/FIG_study2-correlation-summary-bayes.pdf", width = 20, height = 13.5, units = "cm")
```

## Detail plots

```{r}
bayes_corrs_flipped <- bayes_corrs %>% 
  rename(tmp = dimension_x) %>% 
  rename(dimension_x = dimension_y) %>% 
  rename(dimension_y = tmp)
```

```{r}
plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs_flipped, "rigour", "insight")
ggsave("figs/FIG_study2-corr-rigour-insight.pdf", width = 15, height = 12, units = "cm")
```


```{r}
plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs_flipped, "rigour", "simple")
ggsave("figs/FIG_study2-corr-rigour-simple.pdf", width = 15, height = 12, units = "cm")
```

```{r}
plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs_flipped, "rigour", "marks")
ggsave("figs/FIG_study2-corr-rigour-marks.pdf", width = 15, height = 12, units = "cm")
```

```{r}
plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs_flipped, "simple", "marks")
ggsave("figs/FIG_study2-corr-simple-marks.pdf", width = 15, height = 12, units = "cm")
```

```{r}
rigour_vs_marks <- plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs_flipped, "rigour", "marks")
rigour_vs_insight <- plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs_flipped, "rigour", "insight")
rigour_vs_simple <- plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs_flipped, "rigour", "simple") +
  expand_limits(y = 2.5) # this avoids the text label overlapping data points
simple_vs_marks <- plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs, "marks", "simple") + expand_limits(y = 2.5)

library(patchwork)
rigour_vs_insight + rigour_vs_simple + simple_vs_marks + 
  plot_annotation(tag_levels = "a", tag_prefix = '(', tag_suffix = ')')
ggsave("figs/FIG_study2-corr-details.pdf", width = 25, height = 10, units = "cm")

rigour_vs_insight + rigour_vs_simple + 
  plot_annotation(tag_levels = "a", tag_prefix = '(', tag_suffix = ')')
ggsave("figs/FIG_study2-corr-details2.pdf", width = 20, height = 10, units = "cm")

rigour_vs_marks + rigour_vs_insight + rigour_vs_simple + 
  plot_annotation(tag_levels = "a", tag_prefix = '(', tag_suffix = ')')
ggsave("figs/FIG_study2-corr-details3.pdf", width = 25, height = 10, units = "cm")
```

```{r}
r_marks <- plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs, "marks", "rigour")
r_insight <- plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs, "insight", "rigour")
r_simple <- plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs, "simple", "rigour") +
  expand_limits(y = 2.5) # this avoids the text label overlapping data points

r_marks + r_insight + r_simple + 
  plot_annotation(tag_levels = "a", tag_prefix = '(', tag_suffix = ')')
ggsave("figs/FIG_study2-corr-rigour3ways.pdf", width = 25, height = 10, units = "cm")

r_marks + r_simple + 
  plot_annotation(tag_levels = "a", tag_prefix = '(', tag_suffix = ')')
ggsave("figs/FIG_study2-corr-rigour2ways.pdf", width = 20, height = 10, units = "cm")
```

```{r}
plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs, "understanding", "rigour")
```