---
title: "Proof CJ: Study 2 factor analysis"
author: "George Kinnear"
date: "25/03/2021"
always_allow_html: true
output:
  github_document:
    html_preview: false
  html_document:
    toc: false
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path='figs-web/05b-study2-factor-analysis/')

# for plotting
library(ggrepel)
source("functions_for_plotting.R")
theme_set(theme_minimal())
library(patchwork)

library(knitr)
library(kableExtra)
basic_kable = function(df) {
  df %>% 
    kable() %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}

dimensions_sorted <- c("rigour", "insight", "simple", "understanding", "marks")

# For the Bayesian stuff
library(bayestestR)
library(insight)
library(BayesFactor)
ci_width <- 0.95
set.seed(22032021)

# For the factor analysis
library(parameters)
library(see)
library(psych)
library(broom)  # for augment(), tidy()
```

# Data

```{r echo=FALSE, fig.height=1, fig.width=8, message=FALSE}
btm_estimates <- read_csv("data-out/btm_estimates.csv") %>% 
  mutate(dimension = fct_relevel(dimension, dimensions_sorted)) %>% 
  filter(study == "study2") %>% 
  select(-study)

proof_details <- read_csv("proof-details.csv")

params <- btm_estimates %>% 
  select(proof, dimension, theta) %>% 
  pivot_wider(
    names_from = dimension,
    values_from = theta
  )

params %>% 
  basic_kable()
```

```{r, results = "asis"}
params %>% 
  select(-proof) %>% 
  check_factorstructure()

data <- params %>% 
  select(-proof)
```

```{r, results = "asis"}
n <- n_factors(data)
n
```
```{r}
plot(n)
summary(n) %>% basic_kable()
n %>% tibble() %>% basic_kable()
```

```{r, results = "asis"}
fa.parallel(data, fa="fa", fm="ml")
```


# Using `stats::factanal`

```{r}
fitfact <- factanal(data, 2, rotation="varimax")
print(fitfact, digits=3, cutoff=.3, sort=TRUE)
```

```{r}
load <- data.frame(fitfact$loadings[,]) %>%
  rownames_to_column("dimension")

load %>%
  basic_kable()

load %>%
  ggplot(aes(x = Factor1, y = Factor2)) +
  geom_point() +
  geom_text_repel(aes(label = dimension)) +
  expand_limits(x = c(0,1), y = c(0,1)) +
  labs(x = "Factor 1", y = "Factor 2")
```


```{r}
fitfact <- factanal(data, 1, rotation="varimax")
print(fitfact, digits=3, cutoff=.3, sort=TRUE)
```

```{r}
load <- data.frame(fitfact$loadings[,]) %>%
  rownames_to_column("dimension") %>% 
  janitor::clean_names()

load %>%
  basic_kable()

load %>%
  ggplot(aes(x = fitfact_loadings, y = 0)) +
  geom_point() +
  geom_text_repel(aes(label = dimension)) +
  expand_limits(x = c(0,1), y = c(0)) +
  labs(x = "Factor 1")
```

# Using the `psych` package

## 1 factor

```{r warning=FALSE, results = "asis"}
efa1 <- psych::fa(data, nfactors = 1, rotate = "varimax") 
efa1 %>%
  model_parameters(sort = TRUE, threshold = 0.4) %>% 
  display(digits = 3)
```

## 2 factors

```{r warning=FALSE, results="asis"}
efa2 <- psych::fa(data, nfactors = 2, rotate = "varimax") 
efa2 %>%
  model_parameters(sort = TRUE, threshold = 0.4) %>% 
  display(digits = 3)
```

```{r}
load <- efa2 %>%
  model_parameters(sort = TRUE, threshold = 0) %>% 
  janitor::clean_names()

load %>%
  basic_kable()

# Used to produce the table in the paper
load %>%
  select(Dimension = variable, `Factor 1` = mr1, `Factor 2` = mr2) %>% 
  arrange(-abs(`Factor 1`)) %>% 
  #mutate(across(contains("Factor"), ~ ifelse(abs(.) > 0.4, round(., digits = 3), "-"))) %>% 
  mutate(
    across(starts_with("Factor"),
    ~ cell_spec(round(., digits = 3), "latex", bold = if_else(abs(.) > 0.4, T, F))
    )
  ) %>% 
  kable(booktabs = T, escape = F, format = "latex")

load %>%
  ggplot(aes(x = mr1, y = mr2)) +
  geom_point() +
  geom_text_repel(aes(label = variable)) +
  expand_limits(x = c(0,1), y = c(0)) +
  labs(x = "Factor 1", y = "Factor 2")
```

Score for each proof on the two factors:

```{r warning=FALSE}
proof_scores <- predict(efa2 %>%
  model_parameters(sort = TRUE, threshold = 0.4), names = c("F1", "F2")) %>% 
  rownames_to_column("proof")

proof_scores %>% 
  basic_kable()

proof_scores %>%
  ggplot(aes(F1, F2)) +
  geom_point() +
  geom_text_repel(aes(label = proof))
```

# PCA

https://wilkelab.org/SDS375/slides/dimension-reduction-1.html

```{r}
pca_fit <- data %>% 
  scale() %>% 
  prcomp()
```

```{r}
arrow_style <- arrow(
  angle = 20, length = grid::unit(8, "pt"),
  ends = "first", type = "closed"
)
pca_fit %>%
  # extract rotation matrix
  tidy(matrix = "rotation") %>%
  pivot_wider(
    names_from = "PC", values_from = "value",
    names_prefix = "PC"
  ) %>%
  ggplot(aes(PC1, PC2)) +
  geom_segment(
    xend = 0, yend = 0,
    arrow = arrow_style
  ) +
  geom_text(aes(label = column), hjust = -0.1) +
  xlim(-0.1, 1) + ylim(-0.75, 0.75) + 
  coord_fixed()
```

```{r}
pca_fit %>%
  # extract eigenvalues
  tidy(matrix = "eigenvalues") %>%
  ggplot(aes(PC, percent)) + 
  geom_col() + 
  scale_x_continuous(
    # create one axis tick per PC
    breaks = 1:6
  ) +
  scale_y_continuous(
    name = "variance explained",
    # format y axis ticks as percent values
    label = scales::label_percent(accuracy = 1)
  )

pca_fit %>%
  # extract eigenvalues
  tidy(matrix = "eigenvalues") %>% 
  select(PC, percent, cumulative) %>% 
  basic_kable()
```

Location of the proofs on these principal components:

```{r}
pca_fit %>%
  # add PCs to the original dataset
  augment(params) %>%
  rename_with(~ str_remove(., ".fitted")) %>% 
  ggplot(aes(PC1, PC2)) +
  geom_point() +
  geom_text_repel(aes(label = proof))
```

Conjecture:

* PC1 is "convincingness" - 10 (induction) is the most convincing, while 3 (pictorial II), 13 (undetermined coeffs) and 1 (experimental evidence) are least.

* PC2 is "formality" - 10, 11, 12, 13 are all high on that and they are all the most formally written, while 1 and 2 are much more informal.