---
title: "Proof CJ: Study 1 vs Study 2 analysis"
author: "George Kinnear"
date: "22/03/2021"
always_allow_html: true
output:
  github_document:
    html_preview: false
  html_document:
    toc: false
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path='figs-web/06-study1-vs-study2/')

# for plotting
library(ggrepel)
source("functions_for_plotting.R")
theme_set(theme_minimal())

library(knitr)
library(kableExtra)
basic_kable = function(df) {
  df %>% 
    kable() %>%
    kable_styling(bootstrap_options = "striped", full_width = F)
}

dimensions_sorted <- c("rigour", "insight", "simple", "understanding", "marks")

# For the Bayesian stuff
library(bayestestR)
library(insight)
library(BayesFactor)
ci_width <- 0.95
set.seed(22032021)
```


```{r echo=FALSE, message=FALSE}
btm_estimates <- read_csv("data-out/btm_estimates.csv") %>% 
  mutate(dimension = paste(study, dimension)) %>% 
  select(-study)

proof_details <- read_csv("proof-details.csv")
```

# Basic plots of the scales

The scale values with standard errors:

```{r fig.height=3, fig.width=15}
btm_estimates %>% 
  filter(!dimension %in% c("words", "string_length")) %>%
  mutate(dimension = str_replace(dimension, " ", "\n")) %>% 
  mutate(dimension = str_replace(dimension, "study", "Study ")) %>% 
  group_by(dimension) %>% 
  arrange(theta) %>% 
  mutate(order = row_number()) %>% 
  ggplot(aes(x = order, y = theta, ymin = theta - se, ymax = theta + se)) +
  geom_hline(yintercept = 0, colour = "grey") +
  geom_pointrange(size = 0.25) +
  geom_text_repel(aes(label = proof), box.padding = 0.3, min.segment.length = 0.5, colour = "#777777") +
  facet_grid(cols = vars(dimension), scales = "free") +
  theme(
    axis.text.x = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold"),
  ) +
  labs(x = "")
ggsave("figs/FIG_study1vs2-thetas.pdf", width = 30, height = 10, units = "cm")
```


```{r}
# Assemble data
alldims_theta_se <- btm_estimates %>% 
  rbind(
    proof_details %>% 
      select(proof, words, string_length) %>% 
      pivot_longer(
        cols = c("words", "string_length"),
        names_to = "dimension",
        values_to = "theta"
      ) %>% 
      mutate(se = 0)
  )

crossdims <- alldims_theta_se %>% 
  left_join(alldims_theta_se, by = "proof", suffix = c("_x", "_y")) %>% 
  filter(dimension_x != dimension_y)
```


# Bayesian stats

```{r}
dimensions_tbl <- alldims_theta_se %>% select(dimension) %>% distinct() %>% mutate(n = row_number())
upper_triang <- dimensions_tbl %>% 
  rename(dimension_y = dimension, n_y = n) %>% 
  crossing(dimensions_tbl) %>% 
  rename(dimension_x = dimension, n_x = n) %>% 
  filter(n_x > n_y) %>% 
  arrange(n_y, n_x) %>% 
  select(contains("dimension"))

crossdims_upper_triangular <- crossdims %>%
  semi_join(upper_triang, by = c("dimension_x", "dimension_y")) %>% 
  mutate(
    dimension_x = factor(dimension_x, levels = dimensions_tbl$dimension),
    dimension_y = factor(dimension_y, levels = dimensions_tbl$dimension)
  )

# Bayes factor interpretations from van Doorn et al. (2020) https://doi.org/10.3758/s13423-020-01798-5
vandoorn2020 <- effectsize::rules(c(3, 30), c("weak", "moderate", "strong"))
# pick colours for these - avoiding the extremes of the scale, which are too dark
bayes_interp_cols = colorspace::diverging_hcl(8, "Green-Brown")[2:7]
names(bayes_interp_cols) = c("strong in favour of",
                             "moderate in favour of",
                             "weak in favour of",
                             "weak against",
                             "moderate against",
                             "strong against")
```

Do a Bayesian correlation test on each combination, and describe the resulting posteriors.

```{r}
bayes_corrs <- crossdims_upper_triangular %>%
  group_by(dimension_x, dimension_y) %>%
  nest() %>%
  # This step does the Bayesian test.
  # rscale = "ultrawide" specifies uniform (i.e. Beta(1,1)) priors
  mutate(
    model = map(
      data,
      ~ BayesFactor::correlationBF(.$theta_x, .$theta_y, rscale = "ultrawide")
    ),
    posterior = map(model, ~ bayestestR::describe_posterior(., ci = ci_width))
  ) %>%
  select(`dimension_x`, `dimension_y`, posterior) %>%
  unnest(cols = c(posterior)) %>%
  arrange(-BF) %>%
  # interpret Bayes factors in line with van Doorn et al. (2020) https://doi.org/10.3758/s13423-020-01798-5
  mutate(interpretation = effectsize::interpret_bf(BF, rules = vandoorn2020)) %>%
  mutate(interpretation = str_replace(interpretation, "evidence ", "")) %>%
  mutate(interpretation = factor(interpretation, levels = names(bayes_interp_cols)))
```

```{r full-table}
coef_table <- bayes_corrs %>% 
  relocate(interpretation, BF) %>% 
  mutate(hdi = paste0("[", round(CI_low, 2), ", ", round(CI_high, 2), "]")) %>%
  #filter(!dimension_x %in% c("string_length", "words"))
  identity()

coef_table %>%
  select(interpretation,
         BF,
         contains("dimension"),
         Median,
         hdi) %>%
  mutate(Visualisation = "") %>%
  kbl(
    booktabs = T,
    digits = 2,
    col.names = c(
      "Interpretation",
      "BF",
      "Dimension 1",
      "Dimension 2",
      "Median",
      paste0(0.95 * 100, "% HDI"),
      "Visualisation"
    )
  ) %>%
  kable_styling(
    bootstrap_options = "striped",
    full_width = F,
    position = "left"
  ) %>%
  column_spec(
    7,
    image = spec_pointrange(
      x = coef_table$Median,
      xmin = coef_table$CI_low,
      xmax = coef_table$CI_high,
      vline = 0,
      cex = 0.5
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

This shows there is no evidence of the string/word length correlating with the scales, and that there is a reasonable correlation between the scales.

Here is the detail on the correlation between judging scales from the two sessions:

```{r partial-table}
coef_table %>%
  filter(!dimension_x %in% c("string_length", "words")) %>%
  filter(str_detect(dimension_x, "2") & str_detect(dimension_y, "1")) %>% 
  ungroup() %>%
  select(starts_with("dimension"), Median, hdi, BF, interpretation) %>%
  mutate(
    interpretation = paste(interpretation),
    # hack! to convert it to a string
    interpretation = if_else(
      lag(interpretation, n = 1) == (interpretation),
      "",
      interpretation,
      interpretation
    )
  ) %>%
  kbl(
    booktabs = T,
    digits = 2,
    col.names = c(
      "Dimension 1",
      "Dimension 2",
      "Median",
      paste0(ci_width * 100, "% HDI"),
      "BF",
      "Interpretation"
    )
  ) %>%
  kable_styling(full_width = F,
                position = "left")
```

## Summary plots

```{r fig.height=12, fig.width=12, warning=FALSE}
tidy_dimname <- function(dimname) { str_replace(dimname, " ", "\n") %>% str_replace("study", "Study ") }

crossdims_tidynames <- crossdims_upper_triangular %>% 
  mutate(across(
    starts_with("dimension"),
    ~ fct_relabel(., tidy_dimname)
  ))
bayes_corrs_tidynames <- bayes_corrs %>% 
  ungroup() %>% 
  mutate(across(
    starts_with("dimension"),
    ~ fct_relabel(., tidy_dimname)
  ))

plot_bayes_corr_grid(crossdims_tidynames, bayes_corrs_tidynames, r_label = "") +
  theme(legend.position = "bottom")
ggsave("figs/FIG_study1vs2-correlation-summary-bayes-full.pdf", width = 28, height = 35, units = "cm")

plot_bayes_corr_grid(
  crossdims_tidynames %>% filter(!dimension_x %in% c("string_length", "words")),
  bayes_corrs_tidynames %>% filter(!dimension_x %in% c("string_length", "words")),
  r_label = ""
) +
  # increase font sizes for legibility
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 12)
  ) +
  # Tidy up the appearance of the legend - need to style both the fill and colour
  guides(fill = guide_legend(
    ncol = 3,
    byrow = TRUE,
    override.aes = aes(label = "")
  )) +
  guides(colour = guide_legend(ncol = 3, byrow = TRUE))
ggsave("figs/FIG_study1vs2-correlation-summary-bayes.pdf", width = 25, height = 30, units = "cm")
```

## Detail plots

```{r message=FALSE, warning=FALSE}
bayes_corrs_flipped <- bayes_corrs %>% 
  rename(tmp = dimension_x) %>% 
  rename(dimension_x = dimension_y) %>% 
  rename(dimension_y = tmp)
```

```{r message=FALSE, warning=FALSE}
p_rigour <- plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs_flipped, "study1 rigour", "study2 rigour")
#p_rigour + labs(title = "Comparing scales for rigour between studies", x = "Study 1", y = "Study 2")
#ggsave("figs/FIG_study1vs2-corr-rigour.pdf", width = 15, height = 12, units = "cm")
```


```{r message=FALSE, warning=FALSE}
p_insight <- plot_two_dimensions_w_bayes(btm_estimates, bayes_corrs_flipped, "study1 insight", "study2 insight")
#p_insight + labs(title = "Comparing scales for insight between studies", x = "Study 1", y = "Study 2")
#ggsave("figs/FIG_study1vs2-corr-insight.pdf", width = 15, height = 12, units = "cm")
```

```{r message=FALSE, warning=FALSE}
library(patchwork)
(p_rigour + labs(title = "Rigour", x = "Study 1", y = "Study 2")) + (p_insight + labs(title = "Insight", x = "Study 1", y = "Study 2")) &
  theme(plot.title = element_text(size=18))
ggsave("figs/FIG_study1vs2-corr-insight-and-rigour.pdf", width = 20, height = 10, units = "cm")
```
